---
title: "Results and Analysis"
---

###The Formula
```{r, echo=FALSE}
model1<-lm(Share ~ PER + PTS + USG + WS + G + VORP)
model1
```


###Significance Tests of Coefficients
```{r, echo=FALSE}
coeftest(model1, vcov = sandwich)
```

###Analysis of Results

Since many of the same players were included in the dataset (for example, LeBron James received MVP votes in each year of the analysis) and thus the assumption of independence was violated, I had to run the regression under the "sandwich" package in R. Under this package, standard errors are compressed (or "sandwiched") so that tests of significance can be conducted.

Some of the coefficients were statistically significant. VORP was significant at the .10 level, PER was significant at the .05 level, USG was significant at the .01 level, and both G and WS were significant at the .001 level. Most surprising, however, was the fact that some of these variables actually had a negative effect on vote-share. I think this is reflective of the fact that the regression is conducted on a subset of high-performing players. If the whole pool of data from all NBA players were included for each season, I suspect that most of these variables would be positive (though G would likely have little to no effect).

###Limitations and Discussion
As mentioned above, the first limitation that jumps out is the fact that this model is constructed based only on a subset of top-performing players. A model constructed with data from all players would yield different results. In terms of usefulness, a model constructed with data from all players is better because it can be applied to player data each year without having to first carve out an appropriate subset. However, since this is the model I've created, we can see how well it does with the subset of players considered by NBA.com to be the top ten candidates for this year's award (see the "This Year's Race" tab for these results).

Secondly, I mentioned in the Overview section that one of the drivers for voters is team success. The idea is that players who elevate their teams to a level that puts them into position to contend for a championship should be rewarded. Though I included Win Shares, I think a good model should also include team winning percentage as another independent variable. This omission, as well as the omission of data from the whole league for each season, is simply due to the time it would require to compile the data.