---
title: "Results and Analysis"
---

###The Formula
```{r, echo=FALSE}
model1<-lm(Share ~ PER + PTS + USG + WS + G + VORP)
model1
```


###Significance Tests of Coefficients
```{r, echo=FALSE}
coeftest(model1, vcov = sandwich)
```

###Analysis of Results

Since many of the same players were included in the dataset (for example, LeBron James received MVP votes in each year of the analysis) and thus the assumption of independence was violated, I had to run the regression under the "sandwich" package in R. Under this package, standard errors are compressed (or "sandwiched") so that tests of significance can be conducted.

Some of the coefficients were statistically significant. VORP was significant at the .10 level, PER was significant at the .05 level, USG was significant at the .01 level, and both G and WS were significant at the .001 level. This suggests that one part of my hypotheses with respect to these variables was correct: each (though VORP at a lower significance level) had a statistically significant effect on the dependent variable. The lack of a statistically significant coefficient on the other variables means that I am unable to say that they have an effect on the dependent variable.

Most surprising, however, was the fact that some of these variables actually had a negative effect on vote-share. PER and G, the effects of which were both statistically significant, had a negative effect on the dependent variable. The PER result suggests that performing better than your peers can actually hurt your MVP candidacy, which is cause for concern with the model. The G result is interesting as my model would reward exactly the kind of players for whom the statistic was included to weed out: the high-performing players who miss too many games. I am not sure at this time what ought to be done in terms of an adjustment on this front. Perhaps another statistic like minutes played would better capture what I am after. Or, perhaps I am simply wrong to think that the variable is influential for voters.


###Limitations and Discussion
The first limitation that jumps out is the fact that this model is constructed based only on a subset of top-performing players. A model constructed with data from all players would yield different results and I suspect that this helps explain the negative direction of the effect of PER. Within this top-performing subset, a high PER is to be expected so it does not differentiate the candidates as much from one another. If the model was generated from statistics of all NBA players, I would expect my initial prediction of a statistically significant, positive effect to hold. 

A model constructed with data from all players is also better in practice because it can be applied to player data each year without having to first carve out an appropriate subset. However, since this is the model I've created, we can see how well it does with the subset of players considered by NBA.com to be the top ten candidates for this year's award (see the "This Year's Race" tab for these results).

Secondly, I mentioned in the Overview section that one of the drivers for voters is team success. The idea is that players who elevate their teams to a level that puts them into position to contend for a championship should be rewarded. Though I included Win Shares, I think a good model should also include team winning percentage as another independent variable. This omission, as well as the omission of data from all of the players in the league, is simply due to end-of-semester time constraints.